MultiDataProcessPico

### 2023-12-15 Code/MultiDataProcessPico.Rmd
Fixed annotations re:  SS120

Run for each file in a session; all chunks below run for each file.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20221021_PICO_MCMIX006_RUN96_TargetDataMetaFilter.Rds"

@@

SS120 show anomalous jump in OD720 within first 24 h after inoculation.
Therefore we add a filter to remove the first InitialTime  from all SS120 runs.
```{r filter initial data  ProcessData}

@@

# ProcessData <- ProcessData %>%
#   filter(Tube == 1 |
#          Tube == 2 |
#          Tube == 3 & time >= 24 & time <= 125  |
#          Tube == 4 |
#          Tube == 5 |
#          Tube == 6 |
#          Tube == 7 |
#          Tube == 8 )

>>>>

Run for each file in a session; all chunks below run for each file.
```{r read ProcessFile}
ProcessFile <- "../Data/ImportedData/ImportedMCData/20231026_PICO_MCMIX006_RUN126_TargetDataMetaFilter.Rds"

@@

SS120 show anomalous jump in OD720 within first 24 h after inoculation.
Therefore we add a filter to remove the first InitialTime  from anomalous SS120 runs.
```{r filter initial data  ProcessData}

@@

# ProcessData <- ProcessData %>%
#   filter(Tube == 1 |
#          Tube == 2 |
#          Tube == 3  |
#          Tube == 4 |
#          Tube == 5 |
#          Tube == 6 |
#          Tube == 7 |
#          Tube == 8 & time >= 48 & time <= 250)
